---
title: "Final 2"
author: "dane_overholt"
date: "12/12/2019"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align  = "center",
                      fig.height = 3, 
                      fig.width  = 5)
```

```{r}
suppressPackageStartupMessages(library(tidyverse))
```

# Question 1 (10 pts): Nicolas Winding Refn

[Nicolas Winding Refn](https://en.wikipedia.org/wiki/Nicolas_Winding_Refn) is
a Danish film director, most known for his 2011 neo-noir film
[Drive](https://en.wikipedia.org/wiki/Drive_(2011_film)). The data frame in
"refn.RData" contains the following variables

- `film`: The name of the film.
- `genre`: The genre of the film (a factor variable).
- `rt`: The rotten tomatoes score of the film.
- `date`: The release date (a Date variable).
- `weekday`: The day of the week the film was released (a factor variable).

1. (1 pt) Read these data into R using the `load()` function. I'll show you how 
   to do this for a penalty of 1 pt if you are unable to.

```{r}
load("./refn.Rdata")
head(refn)
```     
   

2. (5 pts) The `crime` genre can actually be sub-categorized into `crime thriller` and
   `crime drama`. Use forcats to add these levels to `genre` (which should be a
   factor), then label `Fear X` and `Only God Forgives` to `crime thriller` and 
   the rest of the `crime` films to `crime drama`. Finally, remove the `crime`
   level from `genre`. Print out your new data frame. You don't need to, but you may use `replace()` once you have added the levels if you would like.
   
    It should look like what you see in the handout:
   
    ```{r, eval = TRUE}
    levels(refn$genre)
    
    refn %>%
      mutate(genre = fct_expand(genre, "crime thriller", "crime drama")) -> refn
    
    refn$genre <- c("crime drama",
                    "crime drama",
                    "crime thriller",
                    "crime drama",
                    "crime drama",
                    "crime drama",
                    "action",
                    "action",
                    "crime thriller",
                    "horror")
    
    refn %>%
      mutate(genre = fct_drop(genre, "crime")) -> refn
    
    head(refn, 10)
    ```
    
    
# Question 3 (10 pts): Scrabble Words

Use only functions from the tidyverse. Do **not** try using `str_view()` or 
`str_view_all()` on these data.

1. (2 pts) The data frame in "subscrab.csv" contains a subset of the list of 
   acceptable 2015 Scrabble words. Load this data frame into R. How may words are there in this dataframe?
   
    ```{r}
    words <- read.csv("./subscrab.csv")
    summary(words)
    # 1000 words in the dataframe
    ```
   
2. (4 pts) Find the number of double letters in each word. A double letter
   is a string of length two that has the same letter in each position. So, for
   example, "AALIIS" would have two double letters ("AA" and "II") but 
   "ALAIIS" would only have one ("II").
   
    ```{r}
  words %>%
      mutate(repeats = str_count(word, "([A-Z])\\1")) -> words_repeat
    ```
   
   
3. (2 pts) Plot the distribution of the number of double letters. You will be
   evaluated on the appropriateness of the plot and the aesthetics of the plot.

    ```{r}
words_repeat %>%
      mutate(letters = str_length(word)) -> words_repeat2 
    
words_repeat2 %>%
      ggplot(aes(x = letters, y = repeats, size = repeats)) +
      geom_point() +
      theme_bw() +
      labs(x    = "length",
           y    = "repeats") +
      ggtitle("Length of a Word vs Amount of Double Letters")
    ```
   
4. (2 pts) Of the words that have the most double letters, how many are the longest? How many doubles do they have and what is their length? (you should get more than one word here).

    ```{r}
    words_repeat2 %>%
      group_by(repeats, letters) %>%
      arrange(desc(repeats)) %>%
      arrange(desc(letters)) %>%
      filter(letters >= 15) -> longest
    summary(longest)
    
    # 25 have 3 repeated letters and are length 15
    ```